### 2014-03-07 docs/related-work.tex
Add CensorSpoofer

\documentclass{article} 
\usepackage{url}

@@

To protect the relays from being detected and blocked, a school of research
tries to use covert channels for the communication with relays. FreeWave~\cite{freewave}
encodes data into audio streams and use the Skype P2P network to communicate
with the proxy located outside the censored domain, which is essentially another
Skype client that decodes the stream. The proxy then forward the traffic to the
true destination. A technique known as OSS~\cite{oss}, for ``online scanning
service,'' closely resembles ours in important ways. It uses a third-party web
service as a conduit to carry traffic, encoded either in a URL or in an HTTP
body. Because web services cannot in general be assumed to reproduce a web
server's response exactly (a translation service, for example, returns a
response after translating it to another language), OSS does not use response
bodies to carry data, instead requiring the relay to initiate a reflected
request back to the client. OSS also does not claim that any one service is
difficult to block, rather that there are many web services that can be used.
The main ways in which this work differs is that we effectively control the OSS:
we can count on response bodies being preserved and so use them to send
downstream data; and we put the OSS on infrastructure that is expensive to
block.\\

Traffic using covert channels may exhibit distinguishable characteristics. As
noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
distinguishable from what is regarded as harmless traffic. Therefore, another
school of research focuses on obfuscation techniques for hiding protocol
patterns. One technique is to look unlike anything forbidden by the censor; that
is, fail to match a blacklist. Another is to resemble a protocol that is
explicitly allowed; that is, match a whitelist. Falling into the first category
are ``look-like-nothing'' transports whose payloads are indistinguishable from a
uniformly random byte stream. A examples of such a transport is
obfsproxy~\cite{obfsproxy}, long the go-to obfuscated transport used by Tor.
ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its
payloads, but takes additional steps to obscure its signature of packet lengths
and timing, and is designed to resist active scanning for proxies (the proxy
server says nothing until the client proves knowledge of a shared secret).
Another path to obfsucation is the steganographic approach: look like something
the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker Tunnel (formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor
traffic and attempt to mimic HTTP or Skype traffic.\\

@@

censorspoofer~\cite{censorspoofer} \\

@@

GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App Engine
and Host header--based domain fronting.
GoAgent requires users to upload a personal copy of the server code to App Engine,
and App Engine itself makes HTTP requests, not some proxy farther out.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was then the circumvention tool most used in China,
with 35\% of survey respondants having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%),
and far above that of other special-purpose tools like Tor~(2.9\%)
and Psiphon~(2.5\%).
\\

>>>>

\documentclass{article}  usepackage{url}

@@

To protect the relays from being detected and blocked, a school of research
tries to use covert channels for the communication with relays.
FreeWave~\cite{freewave} encodes data into audio streams and use the Skype P2P
network to communicate with the proxy located outside the censored domain, which
is essentially another Skype client that decodes the stream. The proxy then
forward the traffic to the true destination. CensorSpoofer~\cite{censorspoofer}
decouples the upstream and downstream channel. It assumes the existence of a
low-bandwidth indirect channel that is immune from censorship. It uses this
channel for send requests (URLs) to the proxy while sending dummy requests to a
dummy host. The proxy then fetches the web content and spoofs the dummy host's
IP address to deliver the content back. A technique known as OSS~\cite{oss}, for
``online scanning service,'' closely resembles ours in important ways. It uses a
third-party web service as a conduit to carry traffic, encoded either in a URL
or in an HTTP body. Because web services cannot in general be assumed to
reproduce a web server's response exactly (a translation service, for example,
returns a response after translating it to another language), OSS does not use
response bodies to carry data, instead requiring the relay to initiate a
reflected request back to the client. OSS also does not claim that any one
service is difficult to block, rather that there are many web services that can
be used. The main ways in which this work differs is that we effectively control
the OSS: we can count on response bodies being preserved and so use them to send
downstream data; and we put the OSS on infrastructure that is expensive to
block.\\

Traffic using covert channels may exhibit distinguishable characteristics. As
noted by Winter et al.~\cite{foci12-winter}, Tor traffic is currently
distinguishable from what is regarded as harmless traffic. Therefore, another
school of research focuses on obfuscation techniques for hiding protocol
patterns. One technique is to look unlike anything forbidden by the censor; that
is, fail to match a blacklist. Another is to resemble a protocol that is
explicitly allowed; that is, match a whitelist. Falling into the first category
are ``look-like-nothing'' transports whose payloads are indistinguishable from a
uniformly random byte stream. A examples of such a transport is
obfsproxy~\cite{obfsproxy}, long the go-to obfuscated transport used by Tor.
ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the content of its
payloads, but takes additional steps to obscure its signature of packet lengths
and timing, and is designed to resist active scanning for proxies (the proxy
server says nothing until the client proves knowledge of a shared secret).
Another path to obfsucation is the steganographic approach: look like something
the censor doesn't block. StegoTorus~\cite{stegotorus} and Code Talker Tunnel
(formerly called SkypeMorph)~\cite{skypemorph} camouflage Tor traffic and
attempt to mimic HTTP or Skype traffic. CensorSpoofer also mimics SIP-based VoIP
to hide the upstream channel.\\

@@

@@

GoAgent~\cite{goagent} is a direct inspiration for our work in its use of App
Engine and Host header--based domain fronting. GoAgent requires users to upload
a personal copy of the server code to App Engine, and App Engine itself makes
HTTP requests, not some proxy farther out. According to a May 2013 survey~\cite
{collateral-freedom}, GoAgent was then the circumvention tool most used in
China, with 35\% of survey respondants having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
\\
